\documentclass[minion]{homework}
\doclabel{Math F314: Linear Algebra}
\docdate{Homework 13: Eigenvalues and Eigenvectors}
% \usepackage{cmacros}
\newcommand{\vs}{\mathbf{s}}
\newcommand{\vx}{\mathbf{x}}
\newcommand{\vB}{\mathbf{B}}
\newcommand{\vb}{\mathbf{b}}
\newcommand{\vr}{\mathbf{r}}
\newcommand{\vy}{\mathbf{y}}
\newcommand{\vu}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\vw}{\mathbf{w}}
\newcommand{\vzero}{\mathbf{0}}

\newcommand{\Reals}{\mathbb{R}}
\newcommand{\bbm}{\begin{bmatrix}}
\newcommand{\ebm}{\end{bmatrix}}
\def\vectwo#1#2{\begin{bmatrix}#1\\#2\end{bmatrix}}
\def\vecthree#1#2#3{\begin{bmatrix}#1\\#2\\#3\end{bmatrix}}
\def\vecfour#1#2#3#4{\begin{bmatrix}#1\\#2\\#3\\#4\end{bmatrix}}
\begin{document}
\begin{problems}
\problem For each matrix below, (i) determine its eigenvalues, (ii) determine $N(A-\lambda I_n)$ for every \textbf{real} eigenvalue $\lambda$, and (iii) pick a particular eigenvector associated with every real eigenvalue.
	\begin{subproblems}
	\item $A=\bbm 3&-5\\1&-3\ebm$
	\item $B=\bbm 0&1\\ -1&0\ebm$
	\item $E=\bbm 1&1\\0&1 \ebm$
	\item $C=\bbm 1&2&-1\\1&0&1\\4&-4&5\ebm$
	\item $D$ an $n \times n$ diagonal matrix	
	\end{subproblems}
\problem For matrix $A$ in problem 1 part a, confirm that \textbf{trace}$(A)$ is the sum of the eigenvalues and $\text{det}(A)$ is the product of the eigenvalues.
\problem Suppose $F$ is an upper triangular matrix. Can you easily determine its eigenvalues? Its associated eigenvectors?
\problem This problem refers to matrix $C$ in problem 1 part (d). Note that you should have obtained 3 distinct eigenvalues and picked three distinct associated eigenvectors in part (iii).
	\begin{subproblems}
	\item Explain why you know (without doing any additional computation) that the three eigenvectors you obtained are linearly independent.
	\item Let $P$ be the $3 \times 3$ matrix with the eigenvectors as columns. Explain how you know that $P$ is invertible.
	\item Use a computational tool to find $P^{-1}$.
	\item Use a computational tool to compute $P^{-1}AP.$ What do you observe?
	 
	\end{subproblems}
\problem This problem revisits problem 1 from Homework 11, which is restated below.

\begin{quote}
Below is a system of first-order, linear, differential equations. Rewrite this system in the form $Au=\frac{du}{dt}, \: u=u(0)$ for $t=0.$ (That is, you need to define $u$, $A$, and $u(0).$ You are \emph{not} being asked to solve the system.)

\begin{tabular}{lll}
$\frac{dv}{dt}=4v-5w$&\quad& $v=8$ when $t=0$\\
&&\\
$\frac{dw}{dt}=2v-3w$&\quad& $w=5$ when $t=0$\\
\end{tabular}
\end{quote}
	\begin{subproblems}
	\item Find the eigenvalues of the matrix $A.$
	\item Find an associated eigenvector for each eigenvalue from part (a).
	\item Find the two pure exponential solutions to the differential equation $Au=\frac{du}{dt}$ and verify that they are solutions.
	\item Solve the system $Au=\frac{du}{dt}, \: u=u(0)$ for $t=0.$
	\item Determine $u(5).$
	\item Describe the long-term behavior of $u(t).$
	\end{subproblems}

\end{problems}

\end{document}
