% !TEX TS-program = pdflatexmk
\documentclass[12pt]{article}

% Layout.
\usepackage[top=.75in, bottom=0.75in, left=.75in, right=.75in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,tikz}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl}
\usepackage{enumitem}
%to make tikz pics work
\usepackage{tikz,pgfplots}

\usepackage[colorlinks=true]{hyperref}

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt
\def\tableindent{\hskip 0.5 in}
\def\ts{\hskip 1.5 em}

\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH 663 }}
\rhead{\large\sf\textbf{Fall 2023}}
\chead{\large\sf\textbf{HW 2}}

\newcommand{\localhead}[1]{\par\smallskip\textbf{#1}\nobreak\\}%
\def\heading#1{\localhead{\large\emph{#1}}}
\def\subheading#1{\localhead{\emph{#1}}}

%% Special Math Symbol shortcuts
\newcommand{\bbN}{\mathbb{N}}
\newcommand{\rad}{\text{rad}}
\newcommand{\diam}{\text{diam}}

%\newenvironment{clist}%
%{\bgroup\parskip 0pt\begin{list}{$\bullet$}{\partopsep 4pt\topsep 0pt\itemsep -2pt}}%
%{\end{list}\egroup}%

\usetikzlibrary{calc}
%\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
%middle, xlabel={$x$}, ylabel={$y$}, axis equal }}


\begin{document}
\begin{enumerate}
\item Show that every 2-connected graph contains a cycle.
\item Determine $\kappa(G)$ and $\lambda(G)$ for $G= P^m, \: C^n, \: K^n, \: K_{m,n}$ and the $n$-dimensional cube.
\item Is there a function $f: \mathbb{N} \to \mathbb{N}$ such that, for all $k \in \mathbb{N}$, every graph of minimum degree at least $f(k)$ is $k$-connected?
\item Prove that for every graph non-complete, connected graph $G$, if $F \subseteq E(G)$ is a separating set of edges of minimum order (i.e. $|F| = \lambda (G)$), then $G-F$ has exactly two components.
\item Prove Theorem 1.5.1.\\
\begin{quote}
The following are equivalent for a graph $T.$
\begin{enumerate}	
\item $T$ is a tree.
\item Any two vertices of $T$ are linked by a unique path.
\item $T$ is minimally connected. (That is, $T$ is connected but $T-e$ is disconnected for every $e \in E.$)
\item $T$ is maximally acyclic. (That is, $T$ is acyclic but for every nonadjacent pair of vertices $x,y \in V,$ $T+xy$ contains a cycle.)
\end{enumerate}
\end{quote}
\item Let $F$ and $F'$ be forests on the same vertex set such that $\parallel F \parallel < \parallel F' \parallel.$ Show that $F'$ has an edge $e$ such that $F+e$ is still a forest.
 \end{enumerate}
\end{document}


