% !TEX TS-program = pdflatexmk
\documentclass[12pt]{article}

% Layout.
\usepackage[top=.75in, bottom=0.75in, left=.75in, right=.75in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,tikz}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl}
\usepackage{enumitem}
%to make tikz pics work
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows}
\newcommand{\midarrow}{\tikz \draw[-triangle 90] (0,0) -- +(.1,0);}

\usepackage[colorlinks=true]{hyperref}

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt
\def\tableindent{\hskip 0.5 in}
\def\ts{\hskip 1.5 em}

\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH 663 }}
\rhead{\large\sf\textbf{Fall 2023}}
\chead{\large\sf\textbf{HW 5}}

\newcommand{\localhead}[1]{\par\smallskip\textbf{#1}\nobreak\\}%
\def\heading#1{\localhead{\large\emph{#1}}}
\def\subheading#1{\localhead{\emph{#1}}}

%% Special Math Symbol shortcuts
\newcommand{\bbN}{\mathbb{N}}
\newcommand{\rad}{\text{rad}}
\newcommand{\diam}{\text{diam}}

%\newenvironment{clist}%
%{\bgroup\parskip 0pt\begin{list}{$\bullet$}{\partopsep 4pt\topsep 0pt\itemsep -2pt}}%
%{\end{list}\egroup}%

\usetikzlibrary{calc,arrows.meta}
%\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
%middle, xlabel={$x$}, ylabel={$y$}, axis equal }}


\begin{document}
\begin{enumerate}
\item 
\begin{enumerate}
	\item Find a bipartite graph with a set of preferences such that no matching of maximum size is stable and no stable matching has maximum size. 
	\item Find a non-bipartite graph with a set of preferences that has no stable matching.
\end{enumerate}
\item Give an infinite family of examples that demonstrates that the \emph{bridgeless} hypothesis in Corollary 2.2.2 is necessary.
\item A graph $G$ is called \emph{critically 2-connected} if $G$ is 2-connected but for every edge $e \in E,$ $G-e$ is no longer 2-connected.
	\begin{enumerate}
	\item Find an infinite family of critically 2-connected graphs that are not cycles.
	\item Prove that if $G$ is 2-connected, then the statements below are equivalent:
		\begin{itemize}
		\item $G$ is critically 2-connected.
		\item No cycle in $G$ has a chord.
		\end{itemize}
	\end{enumerate}
\item Prove that the block graph of any connected graph is a tree.
\item Use Menger's Theorem to prove that the statements below are equivalent:
	\begin{itemize}
	\item $G$ is 2-connected.
	\item Every pair of vertices of $G$ lie on a common cycle.
	\item Every pair of edges of $G$ lie on a common cycle. 
	\end{itemize}
\item Given a graph $G=(V,E),$ the \emph{line graph of $G$}, denoted $L(G)$ has vertex set $E$ and two vertice $e,f \in E$ are adjacent in $L(G)$ if and only if $e$ and $f$ are incident in $G$.
	\begin{enumerate}
	\item Determine $L(G)$ for $P^m,$ $G=C^k$ and $H$ (graphed below).\\
	
	%%%BEGIN Graph G
\begin{tikzpicture}[scale=1,every node/.style={draw,circle, inner sep=.05 cm}]
\foreach \i in {0,1,2,3,4}{
	\node (\i) at (\i*72+18:2){};
	}
\node (5) at (27:3){};
\node (6) at (9:3){};
\draw (6)--(0)--(1)--(2)--(3)--(4)--(0)--(5);
\end{tikzpicture}
\item Show that a cut set of vertices in $L(G)$ must correspond to a cut set of edges of $G$, but that the reverse does not necessarily hold.
\end{enumerate}
%%%END Graph G
	
\end{enumerate}
\end{document}