% !TEX TS-program = pdflatexmk
\documentclass[12pt]{article}

% Layout.
\usepackage[top=.75in, bottom=0.75in, left=.75in, right=.75in, headheight=1in, headsep=6pt]{geometry}

% Fonts.
\usepackage{mathptmx}
\usepackage[scaled=0.86]{helvet}
\renewcommand{\emph}[1]{\textsf{\textbf{#1}}}

% Misc packages.
\usepackage{amsmath,amssymb,latexsym}
\usepackage{graphicx,tikz}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx,colortbl}
\usepackage{enumitem}
%to make tikz pics work
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows}
\newcommand{\midarrow}{\tikz \draw[-triangle 90] (0,0) -- +(.1,0);}

\usepackage[colorlinks=true]{hyperref}

% Paragraph spacing
\parindent 0pt
\parskip 6pt plus 1pt
\def\tableindent{\hskip 0.5 in}
\def\ts{\hskip 1.5 em}

\usepackage{fancyhdr}
\pagestyle{fancy} 
\lhead{\large\sf\textbf{MATH 663 }}
\rhead{\large\sf\textbf{Fall 2023}}
\chead{\large\sf\textbf{Midterm 1}}

\newcommand{\localhead}[1]{\par\smallskip\textbf{#1}\nobreak\\}%
\def\heading#1{\localhead{\large\emph{#1}}}
\def\subheading#1{\localhead{\emph{#1}}}

%% Special Math Symbol shortcuts
\newcommand{\bbN}{\mathbb{N}}
\newcommand{\rad}{\text{rad}}
\newcommand{\diam}{\text{diam}}

%\newenvironment{clist}%
%{\bgroup\parskip 0pt\begin{list}{$\bullet$}{\partopsep 4pt\topsep 0pt\itemsep -2pt}}%
%{\end{list}\egroup}%

\usetikzlibrary{calc,arrows.meta}
%\pgfplotsset{my style/.append style={axis x line=middle, axis y line=
%middle, xlabel={$x$}, ylabel={$y$}, axis equal }}


\begin{document}

\textbf{Directions:} 
\begin{itemize}
	\item You have 2 hours to complete all 6 of the problems below. 
	\item Books, notes or other aids are not allowed. 
	\item To receive full credit, proofs must be formal.
	\item Paper will be provided for you. Please put your answer to each problems on a separate sheet of paper.
\end{itemize}

\hrulefill

\begin{enumerate}
\item Prove that a graph is bipartite if and only if every \emph{induced} cycle has even length.
\item 
	\begin{enumerate}
	\item State Tutte's Theorem.
	\item Use Tutte's Theorem to prove that every 3-regular graph with no bridges must have a 1-factor.
	\end{enumerate}
\item Let $G$ be a graph on $n$ vertices. Recall that $\delta(G)$ denotes the minimum degree of $G.$ Prove that if  $\delta(G) \geq (n-1)/2,$ then $G$ must be connected. 
\item Recall that a graph $G$ is critically 2-connected if $G$ is 2-connected by for every $e \in E(G),$ $G-e$ is no longer 2-connected. Prove that every critically 2-connected graph must contain a vertex of degree 2.
\item Suppose $G$ is a connected graph on $n$ vertices. Prove that $G$ has exactly one cycle if and only if $G$ has exactly $n$ edges.
\item Let $G=(V,E)$ be a 2-connected graph. Prove that for every $a \in V$ there exists some $b \in N(a)$ such that $G-a-b$ is still connected. (To be clear, the graph $G-a-b$ is the graph obtained from $G$ by deleting both the vertex $a$ and its neighboring vertex $b.$)
\end{enumerate}

\end{document}